Mechanisms of detachment in fibrillar adhesive systems

### 2022-08-24 review/manuscript.tex
Revised version JTB finished and sent
finished review of JTB referee comments
added new figure for reduction factor with parameter chi
manuscript changed manuscript

Simplifying, we get (see Appendix A for derivation):

@@

The net moment, $M_{net}$, about the joint can be similarly derived
(see Appendix A):

@@

\[
\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{w}
\]

@@

\begin{figure}[H]
\noindent \includegraphics{Reduction_factor-fp}\caption{\textbf{Effect of $\hat{f}_{p}$ on reduction factor.}
Colour plots showing the effect of the dimensionless parameter, $\hat{f}_{p}$,
on the reduction factor for each mode of detachment. Here, we fix
the number of hairs, $N_{t}=25$. All values are normalized to dimensionless
forms, as described in text. \label{fig:Reduction-factor_fp}}
\end{figure}

@@

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{Reduction_factor-Nt}\caption{\textbf{Effect of $N_{t}$ on reduction factor.} 
Colour plots showing the effect of the number of hairs, $N_{t}$, on
the reduction factor for each mode of detachment. Here, we fix the
dimensionless parameter, $\hat{f}_{p}=0.1$. All values are normalized
to dimensionless forms, as described in text. \label{fig:Reduction-factor-Nt}}
\par\end{centering}
\end{figure}

@@

There exists a limit to how much the pad can tilt, depending on its
geometry and material properties. Suppose the hair has a maximum linear
elastic strain limit, $\varepsilon_{m}$, and natural length, $l_{h,0}$.
Based on Figure \ref{fig:Schematic}, if the right most hair is compressed
to its elastic limit, one can derive from simple geometry, that, the
corresponding maximum limit in tilt angle is given by: 
\[
\theta_{limit}=\arctan\frac{l_{h,0}\varepsilon_{m}}{\left(N_{t}-1\right)w}
\]
$\theta_{limit}$ will limit the reduction factor for each of the
detachment mechanisms presented. Longer hairs can result in a lateral
collapse or bundling of hairs, imposing an additional constraint on
$\theta_{limit}$. Large deformation of hairs can also lead to buckling,
which will further limit the reduction in adhesion due to the smaller
effective modulus. Thus, the geometry of the individual hairs is also
crucial in effectively reducing adhesion by \emph{elastic weakening}.
Ideally, hairs with large diameters would be preferable to eliminate
buckling, and optimally long hairs would provide a large range of
angles to which the pad can be tilted while avoiding bundling.

@@

>>>>

Simplifying, we get (see Appendix B for derivation):

@@

The net moment, $M_{net}$, about the joint can be similarly derived
(see Appendix B):

@@

\[
\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{L}
\]

@@

\begin{figure}[H]
\noindent \includegraphics{Reduction_factor-fp}\caption{\textbf{Effect of $\hat{f}_{p}$ on reduction factor.}
Colour plots showing the effect of the dimensionless parameter, $\hat{f}_{p}$,
on the reduction factor for each mode of detachment. Here, we fix
the number of hairs, $N_{t}=25$. The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and 
$\hat{s}=\frac{s}{L}$, as described in text. \label{fig:Reduction-factor_fp}}
\end{figure}

@@

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{Reduction_factor-Nt}\caption{\textbf{Effect of $N_{t}$ on reduction factor.} 
Colour plots showing the effect of the number of hairs, $N_{t}$, on
the reduction factor for each mode of detachment. Here, we fix the
dimensionless parameter, $\hat{f}_{p}=0.1$. The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and $\hat{s}=\frac{s}{L}$, as described in text. \label{fig:Reduction-factor-Nt}}
\par\end{centering}
\end{figure}

Figures \ref{fig:Reduction-factor_fp} and \ref{fig:Reduction-factor-Nt} can be combined into a single set of colour plots by defining a new dimensionless parameter,  $\chi=\hat{f}_{p} N_{t}=\frac{f_{p}N_{t}}{k_{h}w}$ (see Appendix A). Overall, we see that \emph{flex} mode of detachment shows the highest reduction factor among the three modes, with the optimal value of $\chi \sim 1$.

@@

There exists a limit to how much the pad can tilt, depending on its
geometry and material properties. Suppose the hair has a maximum linear
elastic strain limit, $\varepsilon_{m}$, and natural length, $l_{h,0}$.
Based on Figure \ref{fig:Schematic}, if the right most hair is compressed
to its elastic limit, one can derive from simple geometry, that, the
corresponding maximum limit in tilt angle is given by: 
\[
\theta_{limit}=\arctan\frac{l_{h,0}\varepsilon_{m}}{\left(N_{t}-1\right)w}
\]
$\theta_{limit}$ will limit the reduction factor for each of the
detachment mechanisms presented. Longer hairs can result in a lateral
collapse or bundling of hairs, imposing an additional constraint on
$\theta_{limit}$. Large deformation of hairs can also lead to buckling,
which will further limit the reduction in adhesion due to the smaller
effective modulus. Buckling could also, interestingly, promote easier detachment in the \emph{free pull} mode.  
When the compressed hairs at one end of the array buckle, 
there would be an excess clockwise moment in the array system (Figure \ref{fig:Free-pull}). 
This excess moment could subsequently drive the detachment of the remaining hairs.  In the case of biological systems, the ability of an insect to provide the load necessary to tilt and compress its hairy adhesive pad against the surface would further introduce limitations to follow any of the detachment modes discussed here.
All things considered, the geometry and elastic properties of the individual hairs are 
crucial parameters to consider in the design of an optimal array system which shows reversible adhesion via \emph{elastic weakening}.

@@

\section{{Reduction factor: master plot}}

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{Reduction_factor-chi}\caption{\textbf{Effect of $\chi$ on reduction factor.} 
Here, we define a unified dimensionless design parameter $\chi=\frac{f_{p}N_{t}}{k_{h}w}$, combining $\hat{f}_{p}$ and $N_{t}$ into a single number. The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and $\hat{s}=\frac{s}{L}$, as described in text. \label{fig:Reduction-factor-chi}}
\par\end{centering}
\end{figure}
